\texttt{thornado}-transport: a realizability-preserving IMEX scheme for two-moment neutrino transport

### 2018-09-20 Documents/M1/Astronum_2018/sections/Numerical.tex
Updated the figures.

\subsection{Accuracy Tests}
To compare the accuracy of the IMEX scheme, we applied our PDARSs with RKCB2 [citation] and SSP2332[citation] scheme to some smooth problems in streaming, absorption, ans scattering dominated regimes in one spatial dimension.
All the tests in this subsection were applied with third order accurate spatial discretization, the maximum entropy closure in the low occupancy limit and time step $\dt = 0.1 \times \dx $.
More information and the definition of the absolute error and the relative error can be found in \cite{Chu_2018}.

@@

\subsubsection{Neutrino Stationary State Test}
\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.4\textwidth]{figures/NStatinaryS_EOS}
    \includegraphics[width=0.55\textwidth]{figures/NSS_Opacities}
  \end{tabular}
   \caption{Neutrino Stationary State Test}
\end{figure}

\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.45\textwidth]{figures/NSS_0_1}
    \includegraphics[width=0.45\textwidth]{figures/NSS_0_2} \\
    \includegraphics[width=0.45\textwidth]{figures/NSS_1_1}
    \includegraphics[width=0.45\textwidth]{figures/NSS_1_2} \\
    \includegraphics[width=0.45\textwidth]{figures/NSS_3_1}
    \includegraphics[width=0.45\textwidth]{figures/NSS_3_2} \\
    \includegraphics[width=0.45\textwidth]{figures/NSS_5_1}
    \includegraphics[width=0.45\textwidth]{figures/NSS_5_2} \\
  \end{tabular}
   \caption{Neutrino Stationary State Test}
\end{figure}

>>>>

\subsection{Accuracy Tests}
To compare the accuracy of the IMEX scheme, we applied our PDARSs with Cavaglieri \& Bewley \cite{cavaglieriBewley2015} (RKCB2) and Pareschi \& Russo \cite{pareschiRusso_2005} (SSP2332) scheme to some smooth problems in streaming, absorption, ans scattering dominated regimes in one spatial dimension.
All the tests in this subsection were applied with third order accurate spatial discretization, the maximum entropy closure in the low occupancy limit and time step $\dt = 0.1 \times \dx $.
More information and the definition of the absolute error and the relative error can be found in \cite{Chu_2018}.

@@

\subsubsection{Neutrino Stationary State Test}
\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.45\textwidth]{figures/NStatinaryS_EOS}
    \includegraphics[width=0.45\textwidth]{figures/NSS_Opacities}
  \end{tabular}
   \caption{Neutrino Stationary State Test}
\end{figure}

\begin{figure}[h]
  \centering
    \includegraphics[width=\textwidth]{figures/NSS_1_1}\\
    \includegraphics[width=\textwidth]{figures/NSS_3_1} \\
    \includegraphics[width=\textwidth]{figures/NSS_5_1} \\
   \caption{Neutrino Stationary State Test}
\end{figure}

### 2018-09-20 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Updated the figures.

\subsection{Constraints on Moments}
One fundamental fact one should concern before solving the system is the property he/she should never violate.
For a fermionic system, the property is Pauli exclusion principle, or 
\begin{equation}
f \in (0,1).
\end{equation}
As a result, the angular moments as the integrations of $f$ are confined as following
\begin{align}
\cJ \in(0,1), \quad &(1-\cJ)\cJ-|\vect{\cH}|  > 0, \\
  \chi_{\mbox{\tiny min}}
  =\max\big(1-\f{2}{3\cJ},h^{2}\big)
  < & \chi<\min\big(1,\f{1}{3\cJ}-\f{\cJ}{1-\cJ}h^{2}\big)=\chi_{\mbox{\tiny max}},
  \label{eq:eddingtonFactorBounds}
\end{align}
where $h = |\bcH|/\cJ$ is the flux factor.
As Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the constraints on moments all the time: Kershaw [citation], Wilson [citation], Levermore [citation], Minerbo [citation], Janka 2 [citation] may work fine at low occupancy case, but not at high occupancy situation; Janka 1 [citation] is even worse and not work all the time. Only Cernohorsky \& Bludman[citation] among these plotted closures remains in the realizable region.
\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_10}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_90}
  \end{tabular}
   \caption{Plot of Eddington factors $\chi$ versus flux factor $h$ for different values of $\cJ$ for various algebraic closures: $\cJ=0.1$ (left panel, low occupied) and $\cJ=0.9$ (right panel, high occupied).  In each panel we plot the Eddington factors of Kershaw (red), Wilson (yellow), Levermore (green), Minerbo (light blue), Cernohorsky \& Bludman (blue) and Janka (purple and pink) closures.  We also plot $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ defined in Eq.~\eqref{eq:eddingtonFactorBounds} (lower and upper dash black lines, respectively).}
  \label{fig:EddingtonFactorsWithDifferentClosure}
\end{figure}

>>>>

\subsection{Constraints on Moments}
One fundamental fact one should concern before solving the system is the property he/she should never violate.
For a fermionic system, the property is Pauli exclusion principle, or 
\begin{equation}
f \in (0,1).
\end{equation}
As a result, the angular moments as the integrations of $f$ are confined as following
\begin{align}
\cJ \in(0,1), \quad &(1-\cJ)\cJ-|\vect{\cH}|  > 0, \\
  \chi_{\mbox{\tiny min}}
  =\max\big(1-\f{2}{3\cJ},h^{2}\big)
  < & \chi<\min\big(1,\f{1}{3\cJ}-\f{\cJ}{1-\cJ}h^{2}\big)=\chi_{\mbox{\tiny max}},
  \label{eq:eddingtonFactorBounds}
\end{align}
where $h = |\bcH|/\cJ$ is the flux factor.
As Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the constraints on moments all the time: Kershaw\cite{kershaw_1976}, Wilson [citation], Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2 [citation] may work fine at low occupancy case, but not at high occupancy situation; Janka 1 [citation] is even worse and not work all the time. Only Cernohorsky \& Bludman\cite{cernohorskyBludman_1994} among these plotted closures remains in the realizable region.
\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_10}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_90}
  \end{tabular}
   \caption{Plot of Eddington factors $\chi$ versus flux factor $h$ for different values of $\cJ$ for various algebraic closures: $\cJ=0.1$ (left panel, low occupied) and $\cJ=0.9$ (right panel, high occupied).  In each panel we plot the Eddington factors of Kershaw (red), Wilson (yellow), Levermore (green), Minerbo (light blue), Cernohorsky \& Bludman (blue) and Janka (purple and pink) closures.  We also plot $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ defined in Eq.~\eqref{eq:eddingtonFactorBounds} (lower and upper dash black lines, respectively).}
  \label{fig:EddingtonFactorsWithDifferentClosure}
\end{figure}
